MHF SCP Experiment Visualisations

### 2024-08-23 minos/outcomes/MHF_SCP_visualisations.Rmd
Added plots for the mental health risk and lone parent comparison. Lone parent comparison plot showed that we were missing run_id from the summary files, so they will need to be re-run

scen.list.20_100 <- c('baseline', '20UniversalCredit', '40UniversalCredit',
                      '60UniversalCredit', '80UniversalCredit', '100UniversalCredit')
```

@@

  # if (length(scen_list) > 5) {
  #   p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen)) +
  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
  #     geom_line(aes(color = scen), linetype = 'dashed') +
  #     geom_point(aes(color = scen)) +
  #     scale_color_manual(values = palette) +
  #     scale_fill_manual(values = palette) +
  #     xlab('Year') +
  #     ylab('Mean SF-12 Change') +
  #     theme(legend.title = element_blank(),
  #           legend.position = c(0.2, 0.8),
  #           legend.text = element_text(size=5),
  #           legend.key.size = unit(1, 'cm')) +
  #     guides(fill=guide_legend(ncol=2))
  # }

  #          legend.background = element_rect(fill = "white")

  # p2 <- ggplot(plot_data2, aes(x = year, y = SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
  #   geom_smooth()

@@

  # if (length(scen_list) > 5) {
  #   p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen)) +
  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
  #     geom_line(aes(color = scen), linetype = 'dashed') +
  #     geom_point(aes(color = scen)) +
  #     scale_color_manual(values = palette) +
  #     scale_fill_manual(values = palette) +
  #     xlab('Year') +
  #     ylab('Mean SF-12 Change') +
  #     theme(legend.title = element_blank(),
  #           legend.position = c(0.2, 0.8),
  #           legend.text = element_text(size=5),
  #           legend.key.size = unit(1, 'cm')) +
  #     guides(fill=guide_legend(ncol=2))
  # }

@@

@@

```{r}
# scen.list.50 <- c('baseline', '50UniversalCredit')
# UC.gender <- do.call(rbind, generate_df_list('UC_gender', scen.list.50))
```

@@

>>>>

scen.list.20_100 <- c('baseline', '20UniversalCredit', '40UniversalCredit',
                      '60UniversalCredit', '80UniversalCredit', '100UniversalCredit')

scen.list.25_100 <- c('baseline', '25UniversalCredit', '50UniversalCredit',
                      '70UniversalCredit', '100UniversalCredit')
```

@@

@@

@@

```{r "lone_parent_function", include=FALSE}
compare_lone_parent <- function(comparison_scen) {
  scen.list <- c('baseline', comparison_scen)
  UC.lone_parent <- do.call(rbind, generate_df_list('priority_lone_parent', scen.list))

  lone_parent.change <- UC.lone_parent %>%
    select(run_id, sex, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(run_id, sex, year, diff_SF_12)

  lone_parent.confint <- lone_parent.change %>%
    group_by(sex, year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = sex), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

  p2 <- ggplot(data = lone_parent.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

```{r "mental_illness_risk_plots", include=FALSE}
mental_illness_risk_plots <- function(summary_group, scen.list, palette = my_palette) {

  tit <- ' '
  if (summary_group == 'UC_men_illness_risk') { tit <- 'UC Population' }
  if (summary_group == 'UC_families_men_illness_risk') { tit <- 'UC Families' }
  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }

  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
  # summary_group <- 'men_illness_risk'

  #scen.list <- c('baseline', comparison_scen)
  data <- do.call(rbind, generate_df_list(summary_group, scen.list))

  plot_data1 <- data %>%
    filter(mental_health_risk == 'TRUE') %>%
    select(-prop, -mental_health_risk) %>%
    pivot_wider(names_from = scen,
                values_from = count) %>%
    mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
    select(run_id, year, starts_with('diff')) %>%
    pivot_longer(cols = starts_with("diff"),
                 names_sep = '_',
                 names_to = c("diff", "scen"),
                 values_to = 'Count')

  plot_data1_confint <- plot_data1 %>%
    group_by(year, scen) %>%
    summarise(n = n(),
              Mean_Count = mean(Count),
              margin = qt(0.975, df = n - 1) * (sd(Count) / sqrt(n)),
              lower = Mean_Count - margin,
              upper = Mean_Count + margin)

  p1 <- ggplot(plot_data1_confint, aes(x = year, y = Mean_Count, group = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point(aes(color = scen)) +
    scale_color_manual(values = palette) +
    scale_fill_manual(values = palette) +
    xlab('Year') +
    ylab('Mean Change') +
    theme(
        legend.title = element_blank(),  # Remove the legend title
        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
        legend.text = element_text(size = 8),  # Increase the text size for better readability
        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
    ) +
    guides(
        color = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        ),
        fill = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        )
    )

    plot_data_2 <- data %>%
      filter(mental_health_risk == 'TRUE') %>%
      select(-mental_health_risk, -count) %>%
      pivot_wider(names_from = scen,
                  values_from = prop) %>%
      mutate(across(starts_with("£"), ~ . - baseline, .names = "diff_{.col}")) %>%
      select(run_id, year, starts_with('diff')) %>%
      pivot_longer(cols = starts_with("diff"),
                   names_sep = '_',
                   names_to = c("diff", "scen"),
                   values_to = 'Proportion')

    plot_data2_confint <- plot_data_2 %>%
      mutate(Proportion = Proportion * 100) %>%
      group_by(year, scen) %>%
      summarise(n = n(),
              Mean_Proportion = mean(Proportion),
              margin = qt(0.975, df = n - 1) * (sd(Proportion) / sqrt(n)),
              lower = Mean_Proportion - margin,
              upper = Mean_Proportion + margin)

    p2 <- ggplot(plot_data2_confint, aes(x = year, y = Mean_Proportion, group = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point(aes(color = scen)) +
    scale_color_manual(values = palette) +
    scale_fill_manual(values = palette) +
    xlab('Year') +
    ylab('Mean Change (%)') +
    theme(
        legend.title = element_blank(),  # Remove the legend title
        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
        legend.text = element_text(size = 8),  # Increase the text size for better readability
        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
    ) +
    guides(
        color = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        ),
        fill = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        )
    )

@@

@@

## Lone Parent

```{r}
compare_lone_parent(comparison_scen = '25UniversalCredit')
compare_lone_parent(comparison_scen = '50UniversalCredit')
compare_lone_parent(comparison_scen = '70UniversalCredit')
compare_lone_parent(comparison_scen = '100UniversalCredit')
```

# Mental Illness Risk

## Whole Pop

```{r}
mental_illness_risk_plots('men_illness_risk', scen.list = scen.list.25_100)
```

## Families

```{r}
mental_illness_risk_plots('men_illness_risk_families', scen.list = scen.list.25_100)
```

## UC Pop

```{r}
mental_illness_risk_plots('UC_men_illness_risk', scen.list = scen.list.25_100)
```

## UC Families

```{r}
mental_illness_risk_plots('UC_families_men_illness_risk', scen.list = scen.list.25_100)
```
